Notes on robust solvers for systems of coupled multiscale PDEs

### 2019-08-02 solver/problem_omega.tex
work on A1

      \multirow{2}{*}{$\frac{H}{H_0}$} & \multicolumn{4}{c}{$\mathcal{B}$}\\

@@

>>>>

      \multirow{2}{*}{$\frac{H}{H_0}$} & \multicolumn{4}{c}{$\mathcal{B}_{2, \Omega_H}$}\\

@@

At this point we have at our disposal an efficient solver for $\mathcal{A}_2$,
that is a 2$d$-1$d$ subcomponent of the coupled problem \eqref{eq:coupled_weak}.
We now turn attention to the 1$d$-1$d$ component; the idea being that the solver
for the coupled problem in some sense consists of solvers for $\mathcal{A}_2$ and
$\mathcal{A}_1$.
